paper

### 2024-09-27 inst/extdata/paperdata/paper.qmd
.

soma0.5 <- soma[, sample(1:524, 393) , drop = FALSE]

@@

# Set metadata and formula for LimROTS analysis
meta.info <- names(soma0.5@colData@listData)
B <- 1000  # Number of bootstrap samples
K <- dim(soma0.5)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "group_comp"
formula.str <- "~ 0 + group_comp + gender + AGE + CNO"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

@@

saveRDS(soma0.5, "D:/LimROTS/inst/extdata/paperdata/Soma0.5.noPCs.LimROTS.rds")

@@

```{r}
plot(soma0.5$q_values)
hist(soma0.5$q_values)
hist(soma0.5$q_values$qvalues)
hist(soma0.5$FDR)

@@

@@

data <- assay(soma)
formula.str <- "~ 0 + group_comp + gender + AGE + CNO + pc1 + pc2 + pc3 + pc4"
meta.info <- data.frame(colData(soma), check.names = FALSE, row.names = row.names(colData(soma)))
meta.info$sample.id <- NULL
meta.info$CNO <- as.factor(meta.info$CNO)
design.matrix <- model.matrix(formula(formula.str), data = meta.info)
colnames(design.matrix) <- make.names(colnames(design.matrix))
fit <- lmFit(data, design.matrix)
cont_matrix <- makeContrasts("group_comp1-group_comp2",  levels=design.matrix)
fit2 <- contrasts.fit(fit, cont_matrix)
fit.ebayes <- eBayes(fit2, trend=TRUE, robust=TRUE)
limma.result <- topTable(fit.ebayes, coef="group_comp1-group_comp2" , number = "Inf")

@@

length(which(limma.result$adj.P.Val < 0.01))

# Create a volcano plot
ggplot(limma.result, aes(x = logFC, y = -log10(P.Value))) +
  geom_point(alpha = 0.8) +
  theme_bw() +
  labs(title = "Volcano Plot", x = "Log Fold Change", y = "-Log10 q.value", color = "True Positive") +
  scale_color_manual(values = c("grey", "red"))+
  geom_hline(yintercept=-log10(0.05), linetype="dashed", color = "blue")+
  geom_hline(yintercept=-log10(0.01), linetype="dashed", color = "black")
```

>>>>

soma0.5 <- soma[, sample(1:524, 262) , drop = FALSE]

@@

# Set metadata and formula for LimROTS analysis
meta.info <- names(soma0.5@colData@listData)
B <- 1000  # Number of bootstrap samples
K <- dim(soma0.5)[1]/2  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "group_comp"
formula.str <- "~ 0 + group_comp + gender + AGE + CNO"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

@@

saveRDS(soma0.5, "../paperdata/Soma0.5.noPCs.LimROTS.rds")

@@

```{r}
soma0.5 <- readRDS("Soma0.5.noPCs.LimROTS.rds")

plot(soma0.5$q_values)
hist(soma0.5$q_values)
hist(soma0.5$q_values$qvalues)
hist(soma0.5$FDR)

@@

soma.limrots <- readRDS("Soma.noPCs.LimROTS.rds")
soma0.5.limrots <- readRDS("Soma0.5.noPCs.LimROTS.rds")

soma.limrots <- row.names(soma.limrots$data)[which(soma.limrots$q_values$qvalues < 0.05)]
soma0.5.limrots <- row.names(soma0.5.limrots$data)[which(soma0.5.limrots$q_values$qvalues < 0.05)]

length(intersect(soma.sig, soma0.5.sig))
```

@@

soma0.5 <- soma[, sample(1:524, 262) , drop = FALSE]

data <- assay(soma0.5)

formula.str <- "~ 0 + group_comp + gender + AGE + CNO"
meta.info <- data.frame(colData(soma0.5), check.names = FALSE, row.names = row.names(colData(soma0.5)))
meta.info$sample.id <- NULL
meta.info$CNO <- as.factor(meta.info$CNO)
design.matrix <- model.matrix(formula(formula.str), data = meta.info)
colnames(design.matrix) <- make.names(colnames(design.matrix))
fit <- lmFit(data, design.matrix)
cont_matrix <- makeContrasts("group_comp1-group_comp2",  levels=design.matrix)
fit2 <- contrasts.fit(fit, cont_matrix)
fit.ebayes <- eBayes(fit2, trend=TRUE, robust=TRUE)
limma.result.0.5 <- topTable(fit.ebayes, coef="group_comp1-group_comp2" , number = "Inf")

@@

length(which(limma.result.0.5$adj.P.Val < 0.05))

keep_samples <- colData(soma)$CNO != 12
soma <- soma[, keep_samples]

data <- assay(soma)

formula.str <- "~ 0 + group_comp + gender + AGE + CNO"
meta.info <- data.frame(colData(soma), check.names = FALSE, row.names = row.names(colData(soma)))
meta.info$sample.id <- NULL
meta.info$CNO <- as.factor(meta.info$CNO)
design.matrix <- model.matrix(formula(formula.str), data = meta.info)
colnames(design.matrix) <- make.names(colnames(design.matrix))
fit <- lmFit(data, design.matrix)
cont_matrix <- makeContrasts("group_comp1-group_comp2",  levels=design.matrix)
fit2 <- contrasts.fit(fit, cont_matrix)
fit.ebayes <- eBayes(fit2, trend=TRUE, robust=TRUE)
limma.result <- topTable(fit.ebayes, coef="group_comp1-group_comp2" , number = "Inf")

length(which(limma.result$adj.P.Val < 0.05))

length(intersect(which(limma.result.0.5$adj.P.Val < 0.05) , which(limma.result$adj.P.Val < 0.05)))
```
